\newcounter{xp}
\newcounter{ecl}
\newcounter{age}
\newcounter{totalhp}
\newcounter{currenthp}
\newcounter{str}
\newcounter{dex}
\newcounter{con}
\newcounter{int}
\newcounter{wis}
\newcounter{cha}
\newcounter{strmod}
\newcounter{dexmod}
\newcounter{conmod}
\newcounter{intmod}
\newcounter{wismod}
\newcounter{chamod}
\newcounter{sizemod}
\newcounter{initmod}
\newcounter{initmisc} %misc initiative modifier
\newcounter{ac}
\newcounter{touchac}
\newcounter{flatfootedac}
\newcounter{acarmour}
\newcounter{acshield}
\newcounter{acdex}
\newcounter{acsize}
\newcounter{acnatural}
\newcounter{acdeflect}
\newcounter{acmisc}
\newcounter{acmaxdex}
\newcounter{fort}
\newcounter{reflex}
\newcounter{will}
\newcounter{basefort}
\newcounter{baseref}
\newcounter{basewill}
\newcounter{resistancesave}
\newcounter{magicfort}
\newcounter{magicref}
\newcounter{magicwill}
\newcounter{fortmisc}
\newcounter{refmisc}
\newcounter{willmisc}
\newcounter{cmb}
\newcounter{cmd}
\newcounter{cmbmisc}
\newcounter{cmdmisc}
\newcounter{bab}
\newcounter{spellresistance}
\newcounter{lightload}
\newcounter{medload}
\newcounter{heavyload}
\newcounter{money}
\newcounter{casterlevel}

\newcommand{\charname}{Xestilophon}
\newcommand{\charrace}{Aerieborn Halfling}
\newcommand{\charclass}{Ranger (Infiltrator, Divine Tracker 9)}
\newcommand{\charalignment}{NG}
\newcommand{\charsex}{Male}
\newcommand{\charsize}{Small}
\setcounter{sizemod}{-1}
\newcommand{\chartype}{Humanoid (Shapechanger)}
\newcommand{\charheight}{2'8``}
\newcommand{\charweight}{15.42kg/38lb}
\newcommand{\charhair}{Black}
\newcommand{\chareyes}{Red}
\setcounter{age}{35}

\setcounter{xp}{0}
\setcounter{ecl}{1}

\setcounter{totalhp}{84}
\setcounter{currenthp}{84}
\newcommand{\speed}{30', 6sq (medium load)}

                     %       Racial   4th  Belt
\setcounter{str}{14} % 5
\setcounter{dex}{22} % 10     +2*     +1    +2
\setcounter{con}{12} % 2
\setcounter{int}{10} % 0
\setcounter{wis}{16} % 2      +2            +2
\setcounter{cha}{9}  % 1      -2


\setcounter{acnatural}{1}
\setcounter{acarmour}{5}
\setcounter{acmaxdex}{6} %maximum dexterity modifier armour allows. Use a high number for none

\setcounter{basefort}{7}
\setcounter{baseref}{7}
\setcounter{basewill}{3}
\setcounter{resistancesave}{1}
\setcounter{bab}{10}
\setcounter{spellresistance}{0}

\setcounter{cmdmisc}{\value{acdeflect}}

\newcommand{\feats}{
 Endurance$^{b}$, Weapon Focus (Bow)$^{1st}$, Point Blank Shot$^{2nd}$, Precise Shot$^{3rd}$, Rapid Shot$^{5th}$,
 Improved Precise Shot$^{6th}$, Deadly Aim$^{7th}$, Improved Critical (Longbow)$^{9th}$, Clustered Shot$^{10th}$
}

\newcommand{\traits}{
Undead Crusader (+1 damage vs undead, +1 Know(religion)), Magical Knack \\
}
\newcommand{\specialabilities}{
Low-light vision 
1/day Speak with Animals, 1/day Feather Fall
Animal Minded (+2 perception/sense motive)
When shifting: +2 dex, one of (bite 1d6, two talons 1d4, +4 perception, +1 Natural Armour) \\
Combat Style (archery), Swift Tracker
Favoured Enemy (Undead +6), Outsider (evil +2), Humanoid (Human +4), Woodland Stride. \\
100min/day: Adaptation (darkvision 60 ft., Fire resistance 5, Great Fortitude, Iron Will, Lightning Reflexes, natural armor (+2). Skill Focus (Stealth))
Blessings (su; no AoO) (Liberation, Luck) (3+level per day): Liberation (minor): At first level, for one round as a swift
action, you can ignore impediments to your mobility and effects that cause paralysis (as freedom of movement). You can
activate this blessing even if you're otherwise unable to take actions, but not if you're unconscious. \\
Lucky Presence (minor): At 1st level, you can touch an ally and grant it a lucky presence. The target of this luck
can call upon it to roll any one ability check, attack roll, saving throw, or skill check twice and take the better result.
The decision to use this ability must be made before the roll is made. Once used, the effect ends. \\ Evasion
}

\newcommand{\conditionalmods}{
}
\newcommand{\languages}{
Common, Halfling, Ancient Osirion, Draconic \\
}
\setcounter{lightload}{43}
\setcounter{medload}{87}
\setcounter{heavyload}{\value{lightload} + \value{medload}}

\setcounter{money}{4273}

\newcommand{\conditionalspellmods}{
}

\setcounter{casterlevel}{9}  % Level - 3 + 2 (Magical Knack)

\newcommand{\spellsknown}{
}

\newcommand{\domains}{
None
}
\newcommand{\notes}{
Good Dreams (Desna): Your dreams often give you
a hint of possible dangers you might face during your
day-such as a fall, a blast of fire, or a poisonous snake-
and this hint sometimes makes all the difference. Each
time you sleep, the GM tells you of a dangerous dream
you had. Once per day, if you have to make a saving throw
against a threat related or similar to that dream, you can
roll twice and take the more favorable result. If you do
not encounter circumstances similar to the threat or
situation you dreamed, this trait has no effect that day. If
you have the Halfling Jinx trait (see page 27), you cannot
select this trait, and vice versa.

Change Shape (Su, 5 RP): A skinwalker can change shape into a bestial form as a standard action. In bestial form, a skinwalker gains a +2
racial bonus to either Dexterity (already included in stats). While in this form, a skinwalker also takes on an animalistic feature that 
provides a special effect. Each time a skinwalker assumes bestial form, she can choose to gain one of the following features:
\begin{itemize}
 \item 2 claw attacks that each deal 1d4 points of damage
 \item Darkvision to a range of 60 feet.
 \item +1 racial bonus to natural armor.
\end{itemize}
The racial ability score bonus and additional feature last as long as the skinwalker remains in that form, and a skinwalker can remain in
bestial form for as long as she wants. While in bestial form, a skinwalker takes a -4 penalty on Charisma and Charisma-based checks when 
interacting with humanoids that lack the shapechanger subtype.

A skinwalker can return to her humanoid form as a swift action. To change forms and gain a different benefit, a skinwalker must first return 
to her humanoid form then use her shapechange ability again. A skinwalker can shapechange into bestial form a number of times per day equal
to 3 + 1/2 her character level.

Typical spell preparation:
\begin{compactenum}
\item [3rd] \spell{Instant Enemy}
\item [2nd] \spell{Raven's Flight}, \spell{Spike Growth}  % Replace in sandy situations
\item [1st] \spell{Abundant Ammunition}, \spell{Resist Energy}, \spell{Liberating command}  % At level 8, add Resist Energy
\end{compactenum}
}
\newcommand{\people}{
Deaconess Sekek - Priestess of Nethys; gatekeeper of the librarian. \\
Scorpion-Centaur
}



\newcommand{\biography}{
}